---
title: "KMacvittie_Livesession10assignment"
author: "Korey MacVittie"
date: "April 25, 2018"
output:
  html_document:
    df_print: paged
  prettydoc::html_pretty:
    highlight: github
    theme: architect
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)  
library(rvest)    
library(stringr)   
library(rebus)     
library(lubridate)
library(dplyr)
```

### 1. Mental Health Clinics 
```{r}
# a. Load the dataset
load("./N-MHSS-2015-DS0001-data/N-MHSS-2015-DS0001-data-r.rda")
```

```{r}
# b.Create code which lists the State abbreviations without their counts
va <- (levels(mh2015_puf$LST))
head(va)
```


```{r}
# c. Create a listing of the counts of all VA medical centers in the mainland US by state
va <-count(mh2015_puf,LST)
va = va[-c(4,13,14,42,50),]
head(va)
```


```{r}
# c. Convert to a dataframe 
va_med_ctr <- as.data.frame(va)
str(va_med_ctr)
```




```{r}
ggplot(data=va_med_ctr, aes(x=LST, y=n)) +
  geom_bar(stat="identity", fill="steelblue")+
  theme(axis.text.x=element_text(size=rel(0.7), angle=90)) +
  ggtitle("VA Centers in Mainland US") +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(x="State Name",y="Number of VA Facilities")
```



### 2. Cleaning and Bringing in New Features
```{r}
# a. Read statesize.csv into your R environment
statesize <-read.csv("statesize.csv")
str(statesize)
```


```{r}
va_med_ctr <- rename(va_med_ctr, Abbrev = LST)
```


```{r}
va_state <- full_join(va_med_ctr, statesize, by="Abbrev")
```


```{r}
# Created a new csv file that holds merged data
statesize_two <-read.csv("statesize_two.csv")
```


```{r}
# c. Calculate a new variable in your combined data.frame() which indicates the VA hospitals per thousand square miles
statesize_two <-statesize_two %>% select(StateName,SqMiles, Facility) %>% mutate(VA_Norm = Facility/SqMiles)
```

```{r}
# d.Create another ggplot which considers the VAs per square thousand miles,
# rather than just frequency
ggplot(data=statesize_two, aes(x=StateName, y=VA_Norm)) +
  geom_bar(stat="identity", fill="steelblue")+
  theme(axis.text.x=element_text(size=rel(0.8), angle=90)) +
  ggtitle("VA Centers in US (per 1,000 sq miles)") +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(x="State Name",y="VA offices per 1,000 sq miles")
```

###e. What patterns do you see? The smaller states tend to have a higher concentraion of facilities. 
  Smaller states would have a higher concentration, as they have less area - Alaska is literally like
  one-third the size of the continental US, and most of it is trackless wilderness. There does seem to
  be an emphasis on colonial centers and the coasts - both of which make sense, as VAs are probably
  more useful in states that have strong military presence (in terms of bases and such), and thus have
  a higher proportion of the population that would make use of such services.

